Baseline centering problem

### 2018-12-13 paper/tangotd.tex

If the state space is finite, an exact
solution is indeed $E=\R^{\#S}$ with a one-hot representation for $f$,
and the true matrix $\Delta^{-1}$ for $\green$, namely,
\begin{equation}
f(s_2)=\1_{s_2}/\rho(s_2),\qquad
(\green(s_1))_{s_2}=(\Delta^{-1})_{s_1s_2}
\end{equation}
or equivalently, $f(s_2)=\1_{s_2}$ and
$(\green(s_1))_{s_2}=(\Delta^{-1})_{s_1s_2}/\rho(s_2)$. \footnote{The solution to
such representation problems is never unique because $E$ is an arbitrary
space and one may always make a change of basis in $E$. More precisely,
if $B$ is any invertible linear map on $E$, then changing $f\gets Bf$,
$\green\gets (\transp{B})^{-1}\green$ produces a new solution; indeed
this preserves $\green\cdot f$. This may
be useful to ``renormalize'' once in a while, eg setting $f$ to have
unit covariance, which may help with numerical conditioning.} 
But with infinite or continuous state spaces, we have to find a more
compact representation.

@@

@@

$\green$ is basically a model of the world (summed over time). The
difference with ordinary model-based is: $\green$ is trained as a fixed
point, considering all timescales at once. In ordinary model-based, the
model $\tilde P$ obviously commutes with its iterates ($\tilde P^t\tilde
P=\tilde P\tilde P^t$), but does not provide an easy and accurate
representation of the occupation measure $\tilde \Delta^{-1}=\sum_t \tilde P^t$. So even in
the model-based case, the above might be useful.

>>>>

If the state space is finite, an exact
solution is indeed $E=\R^{\#S}$ with a one-hot representation for $f$,
and the true matrix $\Delta^{-1}$ for $\green$, namely,
\begin{equation}
f(s_2)=\1_{s_2}/\rho(s_2),\qquad
(\green(s_1))_{s_2}=(\Delta^{-1})_{s_1s_2}
\end{equation}
or equivalently, $f(s_2)=\1_{s_2}$ and
$(\green(s_1))_{s_2}=(\Delta^{-1})_{s_1s_2}/\rho(s_2)$. \footnote{The solution to
such representation problems is never unique because $E$ is an arbitrary
space and one may always make a change of basis in $E$. More precisely,
if $B$ is any invertible linear map on $E$, then changing $f\gets Bf$,
$\green\gets (\transp{B})^{-1}\green$ produces a new solution; indeed
this preserves $\green\cdot f$. This may
be useful to ``renormalize'' once in a while to help with numerical
conditioning: eg setting $f$ to have
unit covariance, or $f$ and $\green$ to have the same covariance.

Actually the most symmetric solution may be something like
$f(s_2)=\Delta^{-1/2}\1_{s_2}/\rho(s_2)$ and
$\green(s_1)=\transp{(\Delta^{-1/2})}\1_{s_1}$. This may be the fastest
to reach, by splitting eigenvalues of $\Delta$ halfway between $f$ and
$\green$.}
But with infinite or continuous state spaces, we have to find a more
compact representation.

@@

When sampling for the right Bellman equation, it is wasteful to sample a
state $s_2$ and apply a test function $\psi$ if $\psi(s_2)$ is very
small. Instead one may want to sample $s_2$ according to
$\rho_\psi\deq \rho(s_2)\abs{\psi(s_2)}/\E_{\rho}\abs{\psi}$, in which case
$\E_{s_2\sim \rho} f(s_2)\psi(s_2)$ becomes $\E_{s_2\sim \rho_\psi}
f(s_2)(\E_{\rho}\abs{\psi})$. This may significantly reduce variance.

@@

$\green$ is basically a model of the world (summed over time). The
difference with ordinary model-based is: $\green$ is trained as a fixed
point, considering all timescales at once. $\Delta^{-1}$ contains all
paths of all lengths from $s$ to $s'$. In ordinary model-based, the
model $\tilde P$ obviously commutes with its iterates ($\tilde P^t\tilde
P=\tilde P\tilde P^t$), but does not provide an easy and accurate
representation of the occupation measure $\tilde \Delta^{-1}=\sum_t \tilde P^t$. So even in
the model-based case, the above might be useful.

One may also compute something like $\Delta^{-1}_{s,a,s'}$ (paths that start
at $s$ with action $a$ and arrive at $s'$). Unclear if more useful.
